Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex
still working on sec 5

We use an algorithm that selects a fixed size random subset of $\{1,..., \gamma\}$.  Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample_{\gamma, \eta}$.
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \delta_{code})$ code.   Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for the family of point functions over $\zo^\eta\times \mathcal{Z}$.  Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\begin{enumerate}
\item Sample $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
\item If $c_i = 0$:
\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\subitem Set $\rho_i = \mathcal{O}(I_{v_i})$.
\subitem Set $p_i = \rho_i, \lambda_i$.
\item If $c_i = 1$: Sample $r_i \leftarrow U_n$.
\subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
\end{enumerate}
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$
\item For $i=1,..., \ell$:
\begin{enumerate}
\item Parse $p_i$ as $\rho_i, \lambda_i$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
\item Set $v_i' = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
\item If $\rho_i(v_i') = 1$ set $c_i' = 0$.
\item Else set $c_i' = 1$.
\end{enumerate}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.37in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

We first consider calculate $\expe[\dis(V, V')]$ for some desired error tolerance $t$.
Let $\mu$ be a parameter, let $t = \mu(\gamma-\eta)/\eta$ and assume that $\dis(w, w')\leq t$, for any  $i$ one has:
\begin{align*}
\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-i}\right)\\
&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu
\end{align*}
Thus, by setting $\mu = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(V, V')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.  \bnote{stopped here.}

\begin{lemma}
Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.  Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\eta})$ where the probability is over the coins of $\gen$.
\end{lemma}
\begin{proof}
With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^\mu = t'/(2\eta)$. By the Chernoff bound, we have
\begin{align*}
\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \eta}).
\end{align*}
\end{proof}

\begin{corollary}
Let $\eta = \omega(\log n)$ and let $C\subset\zo^\ell$ be a $(\neigh_t, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
\[
\dis(w, w')= \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\frac{\gamma-\eta}{\eta}) = \Theta(\gamma/\eta)
\]
and $(R, P)\leftarrow \gen(w)$, then
\[
\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\eta}) -\delta_{code}= 1-\ngl(n).
\]
That is, \consref{cons:sampling} is correct with overwhelming probability.

\end{corollary}
\subsection{Discussion of \consref{cons:sampling}}
\consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.  The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
gap &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|\\
\end{align*}
That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.  If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.  However, in this setting $gap =\Omega(\gamma)$ and known constructions of information-theoretic fuzzy extractors suffice in this setting.
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

We use an algorithm that selects a fixed size random subset of $\{1,..., \gamma\}$.  Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ and let $r_{sam}$ the number of required coins for $\sample_{\gamma, \eta}$.
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $\mathcal{Z}$ and $\gamma = \Omega(n)$.  Let $\ell = O(\poly(n)) = \omega(\log n)$ and let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.   Let $\eta = \omega(\log n)$ and let $\mathcal{O}$ be a $\ell$-composable virtual grey box obfuscator with auxiliary input for the family of point functions over $\zo^\eta\times \mathcal{Z}$.  Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\begin{enumerate}
\item Sample $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
\item If $c_i = 0$:
\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\subitem Set $\rho_i = \mathcal{O}(I_{v_i})$.
\subitem Set $p_i = \rho_i, \lambda_i$.
\item If $c_i = 1$: Sample $r_i \leftarrow U_{\mathcal{Z}^{\eta}}$.
\subitem Let $p_i = \mathcal{O}(I_{r_i}), \lambda_i$.
\end{enumerate}
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$
\item For $i=1,..., \ell$:
\begin{enumerate}
\item Parse $p_i$ as $\rho_i, \lambda_i$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
\item Set $v_i' = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
\item If $\rho_i(v_i') = 1$ set $c_i' = 0$.
\item Else set $c_i' = 1$.
\end{enumerate}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.37in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\begin{lemma}
Let $n, W$ be as above and Let $C$ be a code that corrects $t'$ $0\rightarrow 1$ bit errors where $t' =\Theta(\ell)$.  Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, if $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.  %That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
\end{lemma}

\begin{proof}
Let $t$ be as stated in the lemma.
We first consider calculate $\expe[\dis(V, V')]$ and then show that the distance between $v$ and $v'$ is rarely much more than this value.  
Let $\mu = -\log(1-t'/(2\ell))/2$ then one has:
\begin{align*}
\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu(\gamma-\eta)/\eta}{\gamma-i}\right)\\
&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{\mu}{\eta}\right) \\
&\geq \left(1-\frac{\mu}{\eta}\right)^{\eta} =\left( \left(1-\frac{\mu}{\eta}\right)^{\eta/\mu}\right)^\mu\geq \frac{1}{4}^\mu\\
& = \left(\frac{1}{4}\right)^{-\log(1-\frac{t'}{2\ell})/2} = 1-\frac{t'}{2\ell}
\end{align*}

With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq  t'/(2\ell)$. By the Chernoff bound, we have
\begin{align*}
\Pr\left[\frac{1}{\ell} \sum_{i=1}^\ell X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\ell} = O(e^{- \ell}).
\end{align*}
Where the last equality holds because $t'/(2\ell) = \Theta(1)$.
\end{proof}

\begin{corollary}
Let $\eta= \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$ let $C\subset\zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$ for $t' = \Theta(\ell)$ and $\delta_{code} = \ngl(n)$.  Then when
\[
\dis(w, w')\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = \Theta(\frac{\gamma-\eta}{\eta}) = \Theta(\gamma/\eta)
\]
and $(R, P)\leftarrow \gen(w)$, then
\[
\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{|\mathcal{Z}|^\eta} - O(2^{-\ell}) -\delta_{code}= 1-\ngl(n).
\]
That is, \consref{cons:sampling} is correct with overwhelming probability.

\end{corollary}

Combining the last two sections, we have that \consref{cons:sampling} is secure and correct:
\begin{theorem}
Let $n$ be a security parameter.
Let $\mathcal{W}$ be the family of $(\alpha = \omega(1), \beta\leq \gamma(1/2-\Theta(1)))$-unordered block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.  Let $\eta = \omega(\log n)$ and $\ell = O(\poly(n)) = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.  Then for $s_{sec} = \poly(n)$ there exists some $\epsilon = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ for
\begin{align*}
t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} \\
\tilde{m} &=|C|\\
\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
\end{align*}
\end{theorem}

\subsection{Discussion of \consref{cons:sampling}}
\consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.  The required entropy of  an unordered block source is $\alpha\times (1-\beta )\times \gamma = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors.
This yields:
\begin{align*}
gap &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |\mathcal{Z}|\\
&= \Theta(\gamma) - \Theta(\gamma/\eta) \log |\mathcal{Z}|\\
\end{align*}
That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for super polynomial size $\mathcal{Z}$ we can set $\eta$ to be super logarithmic and $o(\log |\mathcal{Z}|)$.  If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $\mathcal{Z}$.  However, in this setting $gap =\Omega(\gamma)$ and known information-theoretic fuzzy extractors provide superior performance.
\bibliographystyle{alpha}
\bibliography{crypto}
